Automated Feedback on Student Writing

### 2019-05-12 Classifier_comparison.Rmd
update
updates

---
title: "Designing a Classifier Evaluation Workflow"
date: "2/21/2019"
bibliography: library.bib
biblio-style: apalike
---

@@

The **bag of keywords approach** requires compiling a list of "key terms" that qualifies the type of content in question to a certain topic. If one or more qualifying keywords is present in a document, the document is assigned to the topic. One of the many problems with this approach is that identifying and organizing a list of terms (preferred, alternate, etc.) is labor intensive (much like simple pattern matching), and the natural ambiguity of language (one keyword can have different meanings) causes lots of false positives. This makes the bag of keywords approach not only not scalable, but also inaccurate.

@@

>6.  Social Media Expert: This person can help us understand how has company XYZ has positioned its products in the market. And how are the sentiment of customers changing over time towards company. He is unaware of any kind of details beyond digital marketing. In the past, he has been right 65% of times.

Given the broad spectrum of access we have, we can probably combine all the information and make an informed decision. In a scenario when all the 6 experts/teams verify that it’s a good decision(assuming all the predictions are independent of each other), we will get a combined accuracy rate of:

>>>>

---
title: "Designing a Classifier Evaluation Workflow"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The **bag of keywords approach** requires compiling a list of "key terms" that qualifies the type of content in question to a certain topic. If one or more qualifying keywords is present in a document, the document is assigned to the topic. One of the many problems with this approach is that identifying and organizing a list of terms (preferred, alternate, etc.) is labor intensive (much like simple pattern matching), and the natural ambiguity of language (one keyword can have different meanings) causes lots of false positives. These limitations make the bag of keywords approach both poorly scalable and less accurate.

@@

>6.  Social Media Expert: This person can help us understand how has company XYZ has positioned its products in the market. And how are the sentiment of customers changing over time towards company. He is unaware of any kind of details beyond digital marketing. In the past, he has been right 65% of times.  
Given the broad spectrum of access we have, we can probably combine all the information and make an informed decision. In a scenario when all the 6 experts/teams verify that it’s a good decision(assuming all the predictions are independent of each other), we will get a combined accuracy rate of:

### 2019-05-12 NB_2r2c.Rmd
update
updates

#Train Model, Predict & Evaluate for Subject
This block predicts whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. 
```{r bayes_training}
# Train the classifier on training data, then test on test dataset, and full dataset.
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject, laplace=1)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)
comments_all_pred_subject <- predict(comments_classifier_subject, comments_all)

comments_classifier_structure <- naiveBayes(comments_train, comments_train_labels_structure, laplace=1)
comments_test_pred_structure <- predict(comments_classifier_structure, comments_test)
comments_all_pred_structure <- predict(comments_classifier_structure, comments_all)
```

@@

This block is an **alternative method** to get the same data tables out using ```tidy``` format. It seems much less direct, but may be over-written.
```{r tidy_prediction_table}

@@

#Use mutate to add a proportion of total column. And yes, it calculates based on subgroups rather than whole column.
prop_tally1<-mutate(tidy_tally1, prop = n/sum(n))
prop_tally1<-select(prop_tally1, 1,2,4)
prop_tally2<-mutate(tidy_tally2, prop = n/sum(n))
prop_tally2<-select(prop_tally2, 1,2,4)
prop_tally3<-mutate(tidy_tally3, prop = n/sum(n))
prop_tally3<-select(prop_tally3, 1,2,4)
prop_tally4<-mutate(tidy_tally4, prop = n/sum(n))
prop_tally4<-select(prop_tally4, 1,2,4)

@@

####\  
***

>>>>

#Train Model, Predict & Evaluate for Subject
This block predicts whether a message is likely to be in group 1_basic, 2_writing, 3_technical, or 4_logic. 
```{r bayes_training subject}
# Train the classifier on training data, then test on test dataset, and full dataset.
comments_classifier_subject <- naiveBayes(comments_train, comments_train_labels_subject, laplace=1)
comments_test_pred_subject <- predict(comments_classifier_subject, comments_test)
comments_all_pred_subject <- predict(comments_classifier_subject, comments_all)
```

```{r bayes_training structure}
comments_classifier_structure <- naiveBayes(comments_train, comments_train_labels_structure, laplace=1)
comments_test_pred_structure <- predict(comments_classifier_structure, comments_test)
comments_all_pred_structure <- predict(comments_classifier_structure, comments_all)
```

@@

This block is an **alternative method** to get the same data tables out using ```tidy``` format. It seems much less direct, but may be over-written.

```{r tidy_prediction_table}

@@

#Use mutate to add a proportion of total column. And yes, it calculates based on subgroups rather than whole column.
prop_tally1<-mutate(tidy_tally1, prop = Freq/sum(Freq))
prop_tally1<-select(prop_tally1, 1,2,4)
prop_tally2<-mutate(tidy_tally2, prop = Freq/sum(Freq))
prop_tally2<-select(prop_tally2, 1,2,4)
prop_tally3<-mutate(tidy_tally3, prop = Freq/sum(Freq))
prop_tally3<-select(prop_tally3, 1,2,4)
prop_tally4<-mutate(tidy_tally4, prop = Freq/sum(Freq))
prop_tally4<-select(prop_tally4, 1,2,4)

@@

### 2019-05-12 N_gram_exploration.rmd
updates

---
title: "Initial Exploration"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The first question to answer before making deeper comparisons is, **are word frequencies different between TAs' comments from different sub-categories?** This page describes the methods used for initial exploration of the TA comments dataset.

Results of these analyses are discussed in depth on this page: https://adanieljohnson.github.io/default_website/findings.html

#The Analyses
I ran three different analyses of word use frequency. For simplicity I reduced the analysis to just the four most common comment subjects.

*  __Pearson correlations for word use frequencies__. This method compares the **absolute frequencies** for words found in **ALL** of the Subject sub-categories.
*  __Word frequency differences based on log-odds ratios__. This method highlights terms that are the **most different between sub-categories**. Again, this method compares frequencies for words found in **ALL** of the Subject sub-categories.
*  __N-grams mapping__ (***Draft***). This method identifies text strings, phrases, and terms that are unique (or nearly unique) to one sub-category. Unlike the other two methods, this one does not drop terms which are missing from one or more groups.

#Setup
```{r Libraries_1}
# Call in tidyverse, other required libraries.
library(tidyverse)
library(tidytext)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)

#Pearson Correlations of Word Frequencies
##Are Shared Words Used At Different Frequencies?
This analysis takes all comments from base_data, tokenizes and filters stopwords, then counts and sorts fractional frequencies for each word in each category. **NOTE**: this analysis only compares word use for terms present in ALL sub-categories. If a word is MISSING from **any subcategory**, the data row for that word is pruned from the dataset. This eliminates all unique words in favor of words found in all sub-categories.

```{r}
#Tokenize phrases, remove the stop words listed in R's standard reference file.
base_data_tokenized <- base_data %>% 
  unnest_tokens(word,ta.comment)

#Stopwords removal.  
sortedwords.comments.all <- base_data_tokenized %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]")) %>%
  count(word, word, sort = TRUE) %>%
  ungroup()

#Calculate total # of words
total_words.all <- sortedwords.comments.all %>% 
  summarize(total = sum(n))

#Calculate then append fractional word frequencies.
sortedwords.comments.all.fraction <- sortedwords.comments.all %>% as_tibble() %>% mutate(
  all.fraction = (n*100)/total_words.all$total
  )

#Select SUBSETs of tokenized data based on code.subject: 
base_data_tokenized.basic <- subset(base_data_tokenized, code.subject == "1_basic", select = (1:28))
base_data_tokenized.writing <- subset(base_data_tokenized, code.subject == "2_writing", select = (1:28))
base_data_tokenized.technical <- subset(base_data_tokenized, code.subject == "3_technical", select = (1:28))
base_data_tokenized.logic <- subset(base_data_tokenized, code.subject == "4_logic", select = (1:28))

#For each subset, filter stopwords, count words and total, then calculate frequencies.
sortedwords.basic <- base_data_tokenized.basic %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]")) %>%
  count(word, word, sort = TRUE) %>%
  ungroup()

#Calculate the number of words in total in the subset
total_words.basic <- sortedwords.basic %>% 
  summarize(total = sum(n))

#Mutate table to calculate then append fractional word frequency in the text.
sortedwords.basic.fraction <- sortedwords.basic %>% as_tibble() %>% mutate(
  basic.fraction = (n*100)/total_words.basic$total
)
#Repeats for subset 2
sortedwords.writing <- base_data_tokenized.writing %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]")) %>%
  count(word, word, sort = TRUE) %>%
  ungroup()

total_words.writing <- sortedwords.writing %>% 
  summarize(total = sum(n))

sortedwords.writing.fraction <- sortedwords.writing %>% as_tibble() %>% mutate(
  writing.fraction = (n*100)/total_words.writing$total
)

#Repeats for subset 3
sortedwords.technical <- base_data_tokenized.technical %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]")) %>%
  count(word, word, sort = TRUE) %>%
  ungroup()

total_words.technical <- sortedwords.technical %>% 
  summarize(total = sum(n))

sortedwords.technical.fraction <- sortedwords.technical %>% as_tibble() %>% mutate(
  technical.fraction = (n*100)/total_words.technical$total
)

#Repeats for subset 4
sortedwords.logic <- base_data_tokenized.logic %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]")) %>%
  count(word, word, sort = TRUE) %>%
  ungroup()

total_words.logic <- sortedwords.logic %>% 
  summarize(total = sum(n))

sortedwords.logic.fraction <- sortedwords.logic %>% as_tibble() %>% mutate(
  logic.fraction = (n*100)/total_words.logic$total
)
```

The next block joins the individual data tables for each subset in a larger file using column named 'word'. Columns get confusing names so they are renamed. The graphs compare frequencies for ~770 words that appear in ALL three sub-categories: Writing, Technical, and Logic.

Graphs 1-3 show frequencies in individual groups versus word frequency overall. Generally, frequency of terms in the whole set of comments should be similar to frequency in an individual group (X vs Y positions similar.) However, some terms associated with Logic subgroup (Graph 3) are far from the best-fit line, suggesting they are under-used for comments in that sub-category.

Graphs 4-6 show pair-wise comparisons between sub-categories. Unlike overall frequency, most words are NOT clustered along the best-fit line, suggesting there is still more variation in word use between sub-categories.

```{r}
total <- merge(sortedwords.comments.all.fraction,sortedwords.technical.fraction,by="word") 
total2 <- merge(total,sortedwords.writing.fraction,by="word")
total3 <- merge(total2,sortedwords.logic.fraction,by="word")
#rename lines that were possibly confusing
names(total3)[2] <- "all.count"
names(total3)[4] <- "technical.count"
names(total3)[6] <- "writing.count"
names(total3)[8] <- "logic.count"

#Mutate table to calculate then append fractional word frequency in the text.
total4 <- total3 %>% as_tibble() %>% mutate(
  writing.wt = (writing.count *100)/all.count
)

total5 <- total4 %>% as_tibble() %>% mutate(
  technical.wt = (technical.count *100)/all.count
)

total6 <- total5 %>% as_tibble() %>% mutate(
  logic.wt = (logic.count *100)/all.count
)

#Plot graphs
ggplot(total6, aes(`all.fraction`,`writing.fraction`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")

ggplot(total6, aes(`all.fraction`,`technical.fraction`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")

ggplot(total6, aes(`all.fraction`,`logic.fraction`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")

ggplot(total6, aes(`technical.fraction`,`writing.fraction`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")

ggplot(total6, aes(`logic.fraction`,`writing.fraction`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")

ggplot(total6, aes(`logic.fraction`,`technical.fraction`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")
```

#Log-Odds Ratios of Word Frequencies
##Which Words Are Shared LEAST Between Categories?
Log-odds ratio comparison identifies the words that have the greatest difference in usage between the two groups being compared. This code block is based on a method for comparing word usage frequencies between two separate Twitter users [https://www.tidytextmining.com/twitter.html](described here.) If the words used by TAs in their comments differ between sub-categories, there should be fairly low Pearson correlations between word frequencies.

```{r}
# Isolate table rows to compare. Then reduce larger dataframe to only 2 required columns of data.
frequency_writing <- filter(base_data, code.subject=="2_writing"|code.subject=="3_technical"|code.subject=="4_logic")
frequency_writing.subcolumns <- frequency_writing %>% select(1, 22:23)

# Tokenize phrases, remove stop words listed in standard reference file.
base_data_tokenized <- frequency_writing.subcolumns %>% 
  unnest_tokens(word,ta.comment) %>% 
  anti_join(stop_words)

#At this point the dataframe should have "Unique.Record" in column 1, "code.subject" in column 2, and the unnested "word" in column 3. All columns are class = "character". Stop words listed in the "stop_words" R reference data file have been removed.

#Block below re-organizes the data for comparisons. This pattern sets "2_writing" as the first dataset, then all other data in remaining columns.
#Groups by code.subject, calculated proportional frequency in each group.
#Final step creates 4 columns: word, 2_writing, code.subject, proportion
#Stats need this format to be able to compare 2_writing against other values.
base_data_tokenized_sorted2 <- base_data_tokenized %>% 
  group_by(code.subject) %>%
  count(code.subject, word, sort=TRUE) %>% 
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(code.subject, proportion) %>% 
  gather(code.subject, proportion, `3_technical`:`4_logic`)

#The dataframe called "base_data_tokenized_sorted2" is the final 4-column dataframe for statistical analysis. Individual words are in column 1, "2_writing" frequency is in Column 2, "code.subject" is in column 3, and "proportion" is in column 4. Columns 1 and 3 are class = "character", 2 and 4 are numeric ranges.

#This structure is needed in order to compare word (in Column 1) frequencies for 2. Writing Quality (Column 2) as Y values against the frequencies of those same words (in Column 4) as X axes. WHICH subset of X values to use is coded in Column 3.

#Pearson correlation between frequency of words in 2_writing versus 3_technical and 2_writing versus 4_logic sub-categories.
cor.test(data = base_data_tokenized_sorted2[base_data_tokenized_sorted2$code.subject == "3_technical",], 
         ~ proportion + `2_writing`)

cor.test(data = base_data_tokenized_sorted2[base_data_tokenized_sorted2$code.subject == "4_logic",], 
         ~ proportion + `2_writing`)

coroutput23 <-cor.test(data = base_data_tokenized_sorted2[base_data_tokenized_sorted2$code.subject == "3_technical",], 
         ~ proportion + `2_writing`)
coroutput24 <-cor.test(data = base_data_tokenized_sorted2[base_data_tokenized_sorted2$code.subject == "4_logic",], 
         ~ proportion + `2_writing`)

#Comparing sub-groups 3_technical and 4_logic requires recreating the dataframe in a slightly different format that excludes the data rows for 2_writing.

# Isolate table rows to compare. Then reduce larger dataframe to only 2 required columns of data.
frequency_writing3 <- filter(base_data, code.subject=="3_technical"|code.subject=="4_logic")
frequency_writing.subcolumns3 <- frequency_writing3 %>% select(1, 22:23)

# Tokenize phrases, remove stop words listed in standard reference file.
base_data_tokenized3 <- frequency_writing.subcolumns3 %>% 
  unnest_tokens(word,ta.comment) %>% 
  anti_join(stop_words)

#At this point the dataframe should have "Unique.Record" in column 1, "code.subject" in column 2, and the unnested "word" in column 3. All columns are class = "character". Stop words listed in the "stop_words" R reference data file have been removed.

#Block below re-organizes the data for comparisons. This pattern sets "3_technical" as the first dataset, then all other data in remaining columns.
#Groups by code.subject, calculated proportional frequency in each group.
#Final step creates 4 columns: word, 3_technical, code.subject, proportion
#Stats need this format to be able to compare 3_technical against other values.
base_data_tokenized_sorted3 <- base_data_tokenized3 %>% 
  group_by(code.subject) %>%
  count(code.subject, word, sort=TRUE) %>% 
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  spread(code.subject, proportion) %>% 
  gather(code.subject, proportion,`4_logic`)

#The dataframe called "base_data_tokenized_sorted3" is the final 4-column dataframe for statistical analysis. Individual words are in column 1, "3_technical" frequency is in Column 2, "code.subject" is in column 3, and "proportion" is in column 4. Columns 1 and 3 are class = "character", 2 and 4 are numeric ranges.

#This structure is needed in order to compare word (in Column 1) frequencies for 3_technical (Column 2) as Y values against the frequencies of those same words (in Column 4) as X axes. WHICH subset of X values to use is coded in Column 3.

#Pearson correlation** between the frequency of words in 3_technical versus 4_logic sub-categories.
coroutput34 <-cor.test(data = base_data_tokenized_sorted3[base_data_tokenized_sorted3$code.subject == "4_logic",], 
         ~ proportion + `3_technical`)

broom::tidy(coroutput23)
broom::tidy(coroutput24)
broom::tidy(coroutput34)
```

###Visualizing Frequency Differences Between Sub-Categories

```{r}
#Create groups by code.subject, calculates proportional frequency in each group.
#Final step creates 5 columns: code.subject, n, word, total, frequency.
base_data_tokenized_sorted2 <- base_data_tokenized %>% 
  group_by(code.subject) %>%
  count(code.subject, word, sort=TRUE) %>% 
  left_join(base_data_tokenized %>% 
  group_by(code.subject) %>% 
  summarise(total = n())) %>%
  mutate(freq = n/total)

base_data_tokenized_sorted2v3 <- base_data_tokenized_sorted2 %>% 
  select(code.subject, word, freq) %>% 
  spread(code.subject, freq) %>%
  arrange(`2_writing`,`3_technical`)

ggplot(base_data_tokenized_sorted2v3, aes(`2_writing`,`3_technical`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")
  #ggsave("Freqplot_3vs2.png", width = 10, height = 6)

#Comparing 2 vs. 4.
base_data_tokenized_sorted2v4 <- base_data_tokenized_sorted2 %>% 
  select(code.subject, word, freq) %>% 
  spread(code.subject, freq) %>%
  arrange(`2_writing`,`4_logic`)

ggplot(base_data_tokenized_sorted2v3, aes(`2_writing`,`4_logic`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")
  #ggsave("Freqplot_4vs2.png", width = 10, height = 6)

#Create groups by code.subject, calculates proportional frequency in each group.
#Final step creates 5 columns: code.subject, n, word, total, frequency.
base_data_tokenized_sorted3 <- base_data_tokenized %>% 
  group_by(code.subject) %>%
  count(code.subject, word, sort=TRUE) %>% 
  left_join(base_data_tokenized %>% 
  group_by(code.subject) %>% 
  summarise(total = n())) %>%
  mutate(freq = n/total)

#Set up comparison for 3 vs. 4.
base_data_tokenized_sorted3v4 <- base_data_tokenized_sorted3 %>% 
  select(code.subject, word, freq) %>% 
  spread(code.subject, freq) %>%
  arrange(`2_writing`,`4_logic`)

ggplot(base_data_tokenized_sorted3v4, aes(`3_technical`,`4_logic`)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red")
  #ggsave("Freqplot_4vs3.png", width = 10, height = 6)
```

###Calculating and Plotting Log-Odds Pairs for Subject Sub-Categories

```{r}
word_ratios2v3 <- base_data_tokenized %>%
  count(word, code.subject) %>%
  group_by(word) %>%
  filter(sum(n) >= 10) %>%
  ungroup() %>%
  spread(code.subject, n, fill = 0) %>%
  mutate_if(is.numeric, funs((. + 1) / (sum(.) + 1))) %>%
  mutate(logratio = log(`2_writing`/`3_technical`)) %>%
  arrange(desc(logratio))

word_ratios3v4 <- base_data_tokenized %>%
  count(word, code.subject) %>%
  group_by(word) %>%
  filter(sum(n) >= 10) %>%
  ungroup() %>%
  spread(code.subject, n, fill = 0) %>%
  mutate_if(is.numeric, funs((. + 1) / (sum(.) + 1))) %>%
  mutate(logratio = log(`3_technical`/`4_logic`)) %>%
  arrange(desc(logratio))

word_ratios2v4 <- base_data_tokenized %>%
  count(word, code.subject) %>%
  group_by(word) %>%
  filter(sum(n) >= 10) %>%
  ungroup() %>%
  spread(code.subject, n, fill = 0) %>%
  mutate_if(is.numeric, funs((. + 1) / (sum(.) + 1))) %>%
  mutate(logratio = log(`2_writing`/`4_logic`)) %>%
  arrange(desc(logratio))

word_ratios2v3 %>% 
  arrange(abs(logratio))
word_ratios3v4 %>% 
  arrange(abs(logratio))
word_ratios2v4 %>% 
  arrange(abs(logratio))
```

```{r}
word_ratios2v3 %>%
  group_by(logratio < 0) %>%
  top_n(25, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("log odds ratio (Writing-top/Technical-bottom)") +
  scale_fill_discrete(name = "", labels = c("2_writing", "3_technical"))
  #ggsave("Logplot_2vs3.png", width = 6, height = 10)

word_ratios3v4 %>%
  group_by(logratio < 0) %>%
  top_n(25, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("log odds ratio (Technical-top/Logic-bottom)") +
  scale_fill_discrete(name = "", labels = c("3_technical","4_logic"))
  #ggsave("Logplot_3vs4.png", width = 6, height = 10)

word_ratios2v4 %>%
  group_by(logratio < 0) %>%
  top_n(25, abs(logratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, logratio)) %>%
  ggplot(aes(word, logratio, fill = logratio < 0)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  ylab("log odds ratio (Writing-top/Logic-bottom)") +
  scale_fill_discrete(name = "", labels = c("2_writing", "4_logic"))
  #ggsave("Logplot_2vs4.png", width = 6, height = 10)

>>>>

---
title: "N-gram Frequency Analysis"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

Another comparison looks at frequencies of N-grams between different sub-categories. This page describes the process used for initial exploration of the TA comments dataset.

### 2019-05-12 Text_classifier_models.Rmd
update
updates

---
title: "Text Classification Primer"
date: "2/21/2019"
bibliography: library.bib
biblio-style: apalike
---

@@

1.  Feature selection and engineering (described here)
2.  Topic categorization and modeling (https://adanieljohnson.github.io/default_website/Topic_categorization.html)
3.  Selecting an appropriate text classifier method (https://adanieljohnson.github.io/default_website/Choosing_classifier.html)
4.  Evaluating the outcomes, and improving the classifier ( https://adanieljohnson.github.io/default_website/Improving_classifier.html)

@@

*  Count-based Vectors
	+  Word Count – total number of words in the documents
	+  Character Count – total number of characters in the documents
	+  Punctuation Count – total number of punctuation marks in the documents
	+  Upper Case Count – total number of upper case words in the documents
	+  Title Word Count – total number of consecutive upper case (title) words in the documents
*  Distribution and Frequency Calculations
	+  Average word density of sentences 
	+  Average length of the words used in the documents
	+  TF-IDF
	+  Reading level estimates, readability (described below)
*  Part of Speech Tagging and Frequency Distribution of Tags 
	+ Noun Count
	+ Verb Count
	+ Adjective Count
	+ Adverb Count
	+ Pronoun Count
*  Word Embedding (described below)

@@

*  Word choices (vocabulary range)
*  Lexical diversity (described below)
*  Stance patterns - hedging, booster, generalization words or phrasing 
*  Concision - comparisons of noun phrase density versus comment clause density
*  Cohesion - use of words that are additive (also), countering (however), specify or emphasize (even, both, especially), connecting (former, latter)
*  Civility and uncertainty - language that acknowledges limits of statement, critiques ideas not people, and makes fewer generalizations

@@

Accuracy increases overall as the number of words used increases, and as the number of dimensions increases. Altszyler et al. (2017) studied Word2vec performance in two semantic tests for different corpus size. They found that Word2vec has a steep learning curve, outperforming another word-embedding technique (LSA) when it is trained with medium to large corpus size (more than 10 million words). However, with a small training corpus LSA showed better performance. Additionally they show that the best parameter setting depends on the task and the training corpus. Nevertheless, for skip-gram models trained in medium size corpora, with 50 dimensions, a window size of 15 and 10 negative samples seems to be a good parameter setting.

>>>>

---
title: "Primer of Text Classification"
date: "2/21/2019"
bibliography: library.bib
biblio-style: apalike
---

@@

1.  Feature selection and engineering (*described below*)
2.  Topic categorization and modeling (https://adanieljohnson.github.io/default_website/Topic_categorization.html)
3.  Selecting an appropriate text classifier method (https://adanieljohnson.github.io/default_website/Choosing_classifier.html)
4.  Evaluating the outcomes, and improving the classifier (https://adanieljohnson.github.io/default_website/Improving_classifier.html)

@@

*  Count-based Vectors
	+  Word Count – total number of words in the documents
	+  Character Count – total number of characters in the documents
	+  Punctuation Count – total number of punctuation marks in the documents
	+  Upper Case Count – total number of upper case words in the documents
	+  Title Word Count – total number of consecutive upper case (title) words in the documents
*  Distribution and Frequency Calculations
	+  Average word density of sentences 
	+  Average length of the words used in the documents
	+  TF-IDF
	+  Reading level estimates, readability (*described below*)
*  Part of Speech Tagging and Frequency Distribution of Tags 
	+ Noun Count
	+ Verb Count
	+ Adjective Count
	+ Adverb Count
	+ Pronoun Count
*  Word Embedding (described below)

@@

*  Word choices (vocabulary range)
*  Lexical diversity (*described below*)
*  Stance patterns - hedging, booster, generalization words or phrasing 
*  Concision - comparisons of noun phrase density versus comment clause density
*  Cohesion - use of words that are additive (also), countering (however), specify or emphasize (even, both, especially), connecting (former, latter)
*  Civility and uncertainty - language that acknowledges limits of statement, critiques ideas not people, and makes fewer generalizations

@@

Accuracy increases overall as the number of words used increases, and as the number of dimensions increases. Altszyler et al. [@Altszyler2017] studied Word2vec performance in two semantic tests for different corpus size. They found that Word2vec has a steep learning curve, outperforming another word-embedding technique (LSA) when it is trained with medium to large corpus size (more than 10 million words). However, with a small training corpus LSA showed better performance. Additionally they show that the best parameter setting depends on the task and the training corpus. Nevertheless, for skip-gram models trained in medium size corpora, with 50 dimensions, a window size of 15 and 10 negative samples seems to be a good parameter setting.

### 2019-05-12 Topic_categorization.Rmd
update
updates

*  A limited keywords vocabulary (National Library of Medicine MeSH categories for example)
*  Disciplinary conventions or shared best practices (the Dublin Core is an example)
*  Prior empirical studies
*  The dataset itself, using *de novo* iterative coding. This process is described further here [LINK] and here [LINK].

@@

###Topic Modeling Methods to Identify Features
####Latent Dirichlet Allocation
(LDA) is a common method for generating topic model features. LDA is an iterative model which starts from a fixed number of topics. Each topic is represented as a distribution over words, and each document is then represented as a distribution over topics. Although the tokens themselves are meaningless, the probability distributions over words provided by the topics provide a sense of the different ideas contained in the documents.

>>>>

*  A limited keywords vocabulary (National Library of Medicine MeSH categories for example)
*  Disciplinary conventions or shared best practices (the Dublin Core is an example)
*  Prior empirical studies
*  The dataset itself, using *de novo* iterative coding. This process is described further here: https://adanieljohnson.github.io/default_website/codebook.html

@@

###Topic Modeling Methods to Identify Features
####Latent Dirichlet Allocation
LDA is a common method for generating topic model features. LDA is an iterative model which starts from a fixed number of topics. Each topic is represented as a distribution over words, and each document is then represented as a distribution over topics. Although the tokens themselves are meaningless, the probability distributions over words provided by the topics provide a sense of the different ideas contained in the documents.

### 2019-05-12 aacr.Rmd
updates

There is growing need and interest in using automated feedback as part of writing training. This raises important questions that have not yet been adequately answered:

@@

#Origins of Automated Feedback
Interest in automated feedback on writing emerged in the mid-1960s. Systems have since progressed from basic spelling checkers to syntax-aware spelling and grammar evaluation. More recently, automated essay scoring (AES) systems emerged that can provide feedback on open-response writing. AES systems use natural language processing and machine learning algorithms to produce a score based on syntactic and lexical patterns and features such as sentence length, word frequency and part of speech [@Shermis2010, @Balfour2013].

@@

Despite their limitations, demand remains high for AES systems, and there are ongoing efforts to integrate them into more traditional writing review models [@Balfour2013]. Constructed response assessments reveal more about student thinking and the persistence of misconceptions than do multiple-choice questions. However they require more analysis on the part of the educator, and so are less likely to be used in large-enrollment courses. Urban-Lurain and colleagues developed automated assessment of constructed response (AACR) as a way to give students constructed response test questions and other work that can be graded automatically [@Kaplan2014, @Weston2015, @Ha2015, @Urban-Lurain2015, @Ha2016]. AACR uses a robust and scalable platform for scoring open responses to pre-written prompts that probe important disciplinary concepts from biology and biological chemistry. The prompts are administered via online course management systems where students enter responses. Lexical and statistical analyses then predict what expert ratings would be for student responses. Work to date shows that automated analyses can predict expert ratings of students' work on these topics accurately and with higher inter-rater reliability than a group of trained human graders. The AACR model is growing rapidly to include additonal STEM disicplines and has a national presence (http://create4stem.msu.edu/project/aacr).

>>>>

There is growing need and interest in using automated feedback as part of writing training. This raises several questions that have not yet been adequately answered:

@@

#Origins of Automated Feedback
Interest in automated feedback on writing emerged in the mid-1960s. Systems have since progressed from basic spelling checkers to syntax-aware spelling and grammar evaluation. More recently, automated essay scoring (AES) systems emerged that can provide feedback on open-response writing. AES systems use natural language processing and machine learning algorithms to produce a score based on syntactic and lexical patterns and features such as sentence length, word frequency and part of speech [@Shermis2010; @Balfour2013].

@@

Despite their limitations, demand remains high for AES systems, and there are ongoing efforts to integrate them into more traditional writing review models [@Balfour2013]. Constructed response assessments reveal more about student thinking and the persistence of misconceptions than do multiple-choice questions. However they require more analysis on the part of the educator, and so are less likely to be used in large-enrollment courses. Urban-Lurain and colleagues developed automated assessment of constructed response (AACR) as a way to give students constructed response test questions and other work that can be graded automatically [@Kaplan2014; @Weston2015; @Ha2015; @Urban-Lurain2015; @Ha2016]. AACR uses a robust and scalable platform for scoring open responses to pre-written prompts that probe important disciplinary concepts from biology and biological chemistry. The prompts are administered via online course management systems where students enter responses. Lexical and statistical analyses then predict what expert ratings would be for student responses. Work to date shows that automated analyses can predict expert ratings of students' work on these topics accurately and with higher inter-rater reliability than a group of trained human graders. The AACR model is growing rapidly to include additonal STEM disicplines and has a national presence (http://create4stem.msu.edu/project/aacr).
